Windowed least-squares model reduction for dynamical systems

### 2019-10-18 main.tex
update

\subsection{Outstanding challenges}
This work seeks to overcome the limitations of existing residual-minimizing
model-reduction methods, and to provide a unifying framework from which
exisiting methods can be assessed. Specifically, we look to overcome the
complex dependence of LSPG on the time discretization,
exponential time growth of the error bounds for Galerkin and LSPG,
the cubic dependence of the computational cost of ST-LSPG on the number of
degrees of freedom, and the lack of ability for ST-LSPG to perform prediction
in time. We now describe the proposed \methodNameLower\ \approachKwd\ for this
purpose. 
%\end{comment}
%\input{formulation_3}

@@

\section{Conclusions}\label{sec:conclude}
This paper introduced the windowed least-squares (\methodAcronym) \approachKwd\ for model reductio\  of dynamical systems. The approach sequentially minimizes the time-continuous full-order model residual within a low-dimensional trial subspace over a series of time windows. The formulation is applicable to both spatial and space--time dimension reduction trial subspaces. The Galerkin, Least-Squares Petrov--Galerkin (LSPG) and space--time LSPG methods were shown to be specific instances of the proposed method

>>>>

\subsection{Outstanding challenges}
This work seeks to overcome the limitations of existing residual-minimizing
model-reduction methods, and to provide a unifying framework from which
existing methods can be assessed. Specifically, we look to overcome the
complex dependence of LSPG on the time discretization,
exponential time growth of the error bounds for Galerkin and LSPG,
the cubic dependence of the computational cost of ST-LSPG on the number of
degrees of freedom, and the lack of ability for ST-LSPG to perform prediction
in time. We now describe the proposed \methodNameLower\ \approachKwd\ for this
purpose. 
%\end{comment}
%\input{formulation_3}

@@

\section{Conclusions}\label{sec:conclude}
This paper introduced the windowed least-squares (\methodAcronym) \approachKwd\ for model reduction  of dynamical systems. The approach sequentially minimizes the time-continuous full-order model residual within a low-dimensional trial subspace over a series of time windows. The formulation is applicable to both spatial and space--time dimension reduction trial subspaces. The Galerkin, Least-Squares Petrov--Galerkin (LSPG) and space--time LSPG methods were shown to be specific instances of the proposed method

### 2019-10-18 section4/spacetime_numerical.tex
update

>>>>

\KTC{It would be great to a comment about how this is equivalent to Qiqi Wang
and Paul Constantine's method in the case of one time window and $\Pi^1$
corresponding to full solution trajectories. They use collocation-based
hyper-reduction at a few points in time (but for the full ODE residual at that
time), which you could mention. This is a very cool connection I didn't
realize before, and I think it's definitely worth mentioning!}
